\section{Appendix Individual Assignment 0741516}\label{app:indivjasper}
\textbf{Since the fuel station has not been built yet, changes in the layout may still be made. What change would you suggest to Bill, if you do not have to care about the cost of such a change?}\\
\\
When we were modeling the fuel station as described in the assignment we quickly found a bottleneck in the lanes. Every three lanes have to be served by only one single cashier. This means the three lanes have to merge into one single lane. So instead of just moving forward to the cashier when you are done refueling you first have to check whether these spots in front of you are free. If not you have to wait and you still bock the pump so all the other vehicles behind you also have to wait. It would be very convenient if we have a solution which makes sure that every lane gets its own kind of cashier, such that you do not have to wait on other lanes when you are done refueling.\\
A straightforward method would be to just give all the lanes a cashier, but this is very expensive so we wont do this. Instead we will use a more intelligent system. This system is also used in other countries and is also know as the "unattended fuel station". This means that a pump is provided with a system that accepts debit cards such that you first enter your debit card and next you refuel and after that you pay with your debit card and you get the card back and can continue on the road again. \\
The idea is now that from every set of three lanes, the central lane still has a cashier, where a customer can still pay in cash or with a debit card and the other two get the debit card system. In this way all the lanes have their own (virtual) cashier and customers are no longer depending on other lanes considering the payment. The throughput of the whole fuel station will be much larger, in this way. Note that in front of each queue there must be a sign which tells the customer if the pump is a debit card only pump or that you can pay in cash (the line with the real cashier).\\
The reason we still have cashiers and not only these debit card pumps is that cashiers also have to do some restocking and when a customer needs help he or she can still join the lane with the real customer. Also there would be no supervision when there are only debit card pumps. Another great advantage of this system is that the lanes which have a debit card system can always stay open. This means that Bill is also able to chose that he will only open the pumps with this system and keeps one cashier on duty for restocking and all the other things the pump cant do itself. This means Bill is able to schedule less cashiers and this means more profit for Bill.